Updates on the Exoplanet Orbit Database

### 2014-03-06 draft/ms.tex
Revision of Introduction with added references.

% Recent development in exoplanet discoveries
Since the first peer-reviewed list of exoplanets with robust orbits
\citep{Butler2002,Butler2006}, the count of exoplanets has increased
from less than 200 to over 1490 as of March 2014
(exoplanets.org). Before the launch of NASA's \kepler\ mission
\citep{Borucki2010}, most confirmed exoplanets were discovered via the
precise radial velocity (RV) method. However, since 2009, \kepler\ has
contributed over $\sim$ 800 confirmed exoplanets
\citep[e.g.,][]{Rowe2014} as well as over 3000 exoplanet candidates
(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).

% The business of tracking planet discoveries
As the number of exoplanet discoveries keeps rising, it is important
to keep track of these discoveries and cataloging the orbital
parameters and host star properties of exoplanet systems. There are
several entities that are devoted to this effort, including the
Exoplanet Orbit Database (EOD) and Exoplanets Data Explorer\footnote{See
  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and so on.

% What is this paper about
This paper describes the continuing efforts since \cite{Wright2011} to
maintain the EOD and the Exoplanets Data Explorer at
exoplanets.org. The EOD has expanded to include all robustly-detected
exoplanets (around {\it any} type of host star) with well-determined
orbital parameters published in peer-reviewed literature. It has also
ingested more parameters of the exoplanet systems and host stars, and
some parameters are revised or deleted. We describe the updates with
the EOD in Section~\ref{sec:update}.

% also the website
We also describe the updates to the website that hosts the EOD and the
Exoplanet Data Explorer, exoplanets.org. As one of the mostly visited
exoplanet database, exoplanets.org had $47,000$ visitors in 2013
according to Google Analytics. The Exoplanet Data Explorer has
expanded its scope and now includes the \kepler\ exoplanet
candidates. We describe these changes in Section~\ref{sec:kepler}. The
website has also gone through major back-end changes since
\cite{Wright2011}, which is described in Section~\ref{sec:website}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}
Make sure to cite \cite{Wright2013} for the definition of orbital elements.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}\label{sec:website}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future}\label{sec:conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
\input{references.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table
\clearpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{CJK*}

>>>>

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates(\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
surpassed the radial velocity (RV) method and become the most fruitful
mean for detecting exoplanets. Meanwhile, great promises lie within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer to keep track of the exoplanet
discoveries and catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted by exoplanets.org, which also hosts the Exoplanets
Data Explorer, an interactive table with plotting tools including all
the EOD exoplanets as well as other confirmed exoplanets (and now also
KOIs). The entire dataset of exoplanets.org is available for download
as a single {\tt .csv} file at the website's front page.\footnote{At
  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet researches (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visitors in 2013
according to Google Analytics.

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope and we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters of the exoplanet systems and host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. We also describe the updates to the
hosting website, exoplanets.org. The Exoplanet Data Explorer at
exoplanets.org has expanded its scope and now includes the
\kepler\ exoplanet candidates (KOIs). We describe these changes in
Section~\ref{sec:kepler}. The website has also gone through major
back-end changes since \cite{Wright2011}, which is described in
Section~\ref{sec:website}.

%------------------------------------------------------------------
% RECYCLE BIN
\begin{comment}
Since the first peer-reviewed list of exoplanets with robust orbits
\citep{Butler2002,Butler2006}, the count of exoplanets has increased
from less than 200 to over 1490 as of March 2014
(exoplanets.org). Before the launch of NASA's \kepler\ mission
\citep{Borucki2010}, most confirmed exoplanets were discovered via the
precise radial velocity (RV) method. However, since 2009, \kepler\ has
contributed over $\sim$ 800 confirmed exoplanets (e.g.,
\ciatealt{Marcy2014}, \citealt{Rowe2014}) as well as over 3000
exoplanet candidates (\kepler\ Objects of Interest, KOIs;
e.g.~\citealt{Batalha2013}).

As the number of exoplanet discoveries keeps rising, it is important
to keep track of these discoveries and cataloging the orbital
parameters and host star properties of exoplanet systems. There are
several entities that are devoted to this effort, including the
Exoplanet Orbit Database (EOD) and Exoplanets Data Explorer\footnote{See
  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and so on.

This paper describes the continuing efforts since \cite{Wright2011} to
maintain the EOD and the Exoplanets Data Explorer at exoplanets.org.

The efforts of keeping track of exoplanet discoveries are being
carried out by several entities, and most notably, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and the Exoplanet Orbit Database (EOD) and
Exoplanets Data Explorer\footnote{See \url{http://exoplanets.org}.}
\citep{Wright2011}.
\end{comment}
%------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}
Make sure to cite \cite{Wright2013} for the definition of orbital elements.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}\label{sec:website}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future}\label{sec:conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
\input{references.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table
\clearpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{CJK*}
